Dynamic Walking and Whole-Body Motion Planning for Humanoid Robots: an Integrated Approach

### 2012-12-04 paper.tex
Address review concerning fast dynamic walking motion.

>>>>

\textbf{Relying on the cart-table model approximation means that the
  angular momentum induced by arm movements for instance can lead to
  non dynamically balanced walking motion. We thus implement the ZMP
  filtering stage proposed in \cite{kajita2003biped} to compute the
  exact ZMP and take into account the full dynamics of the robot and
  generate feasible trajectories.}
